### 2020-12-17 written/SC_model/SC_model.tex

\thispagestyle{plain}
\begin{center}                  % Center the following lines
{\Large Draft of new SC section} \\
Sean Bittner and Alex Piet \\
December 11, 2020 \\
\end{center}

\section{Identifying neural mechanisms of flexible task switching} \label{results_SC}
In a rapid task switching experiment \cite{duan2015requirement}, rats were explicitly cued on each trial to either orient towards a visual stimulus in the Pro (P) task or orient away from a visual stimulus in the Anti (A) task (Fig. \ref{fig:SC}A). 
Neural recordings in the midbrain superior colliculus (SC) exhibited two populations of neurons that simultaneously represented both task context (Pro or Anti) and motor response (contralateral or ipsilateral to the recorded side): the Pro/Contra and Anti/Ipsi neurons \cite{duan2018collicular}.
Duan et al. proposed a model of SC that, like the V1 model analyzed in the previous section, is a four-population dynamical system.  
We analyzed this model, where the neuron-type populations are functionally-defined as the Pro- and Anti-populations in each hemisphere (left (L) and right (R)), their connectivity is parameterized geometrically  (Fig. \ref{fig:SC}B).
The input-output function of this model is chosen such that the population responses $\mathbf{x} = [x_{LP}, x_{LA}, x_{RP}, x_{RA}]^\top$ are bounded from 0 to 1 as a function $f$ of a dynamically evolving internal variable $\mathbf{u}$.
The dynamics evolve with timescale $\tau=0.09$ governed by connectivity weights $W$
\begin{equation}
\begin{split}
\tau \frac{d\mathbf{u}}{dt} &= -\mathbf{u} + W\mathbf{x} + \mathbf{h} + d\mathbf{B} \\
\mathbf{x} &= f(\mathbf{u})
\end{split}
\end{equation}
with white noise of variance $\epsilon^2 = 0.2^2$.
The input $\mathbf{h}$ is comprised of a cue-dependent input to the Pro or Anti populations, a stimulus orientation input to either the Left or Right populations, and a choice-period input to the entire network (see Section \ref{methods_SC}).
Here, we use EPI to determine the changes in network connectivity $\mathbf{z} = [sW, vW, dW, hW]^{\top}$ resulting in execution of rapid task switching behavior.

@@

We define rapid task switching behavior as accurate execution of each task.  Inferred models should not exhibit fully random responses (50\%), or perfect performance (100\%), since perfection is never attained by even the best trained rats.
We formulate rapid task switching as an emergent property by stipulating that the average accuracy in the Pro task $p_P(\mathbf{x}, \mathbf{z})$ and Anti task $p_A(\mathbf{x}, \mathbf{z})$ be $75\%$ with variance $5\%^2$.
\begin{equation}\label{eq:EP}
\begin{split}
\mathcal{X} ~~:~~ \mathbb{E}_{\mathbf{z}}\begin{bmatrix} p_P(\mathbf{x}; \mathbf{z}) \\ p_A(\mathbf{x}; \mathbf{z}) \end{bmatrix}  &~~=~~  \begin{bmatrix} 75\% \\ 75\% \end{bmatrix}  \\ 
 \text{Var}_{\mathbf{z}}\begin{bmatrix} p_P(\mathbf{x}; \mathbf{z}) \\ p_A(\mathbf{x}; \mathbf{z}) \end{bmatrix}  &~~=~~  \begin{bmatrix} 5\%^2 \\ 5\%^2  \end{bmatrix}
\end{split}
\end{equation}
A variance of $5\%$ performance in each task will confer a posterior producing performances ranging from about $65\%-85\%$, allowing us to examine the properties of connectivity that yield better performance.

@@

In agreement with experimental results form Duan et al., we found that inactivation above nominal strength during the delay period consistently decreased performance in the Anti task, but had no consistent effect on the Pro task (Fig. \ref{fig:SX3}), e.g. (Fig. \ref{fig:SC}D, bottom).
Interestingly, the trends in eigenvalues that result in greater $p_A$ increase the error from delay period inactivation in the Anti task ($p_A - p_{A, opto}$) (Fig. \ref{fig:SC}E.
Despite these opposing effects, $p_A$ is uncorrelated with ($p_A - p_{A, opto}$), while $p_P$ is correlated (Fig. \ref{fig:SX4}).
This shows that the degree of error introduced by delay period inactivation is controlled by the dynamical mechanisms controlling success in the Pro task (namely $\lambda_{\text{task}}$ and $\lambda_{\text{side}}$).
Such comparable dynamics between the non-inactivated Pro task and the delay period inactivated Anti task are salient in simulations (Fig. \ref{fig:SC}D top-left and bottom-right).

>>>>

\thispagestyle{plain}
\begin{center}                  % Center the following lines
{\Large Draft of new SC section} \\
Sean Bittner and Alex Piet \\
December 14, 2020 \\
\end{center}

\section{Identifying neural mechanisms of flexible task switching} \label{results_SC}
In a rapid task switching experiment \cite{duan2015requirement}, rats were explicitly cued on each trial to either orient towards a visual stimulus in the Pro (P) task or orient away from a visual stimulus in the Anti (A) task (Fig. \ref{fig:SC}A). 
Neural recordings in the midbrain superior colliculus (SC) exhibited two populations of neurons that simultaneously represented both task context (Pro or Anti) and motor response (contralateral or ipsilateral to the recorded side): the Pro/Contra and Anti/Ipsi neurons \cite{duan2018collicular}.
Duan et al. proposed a model of SC that, like the V1 model analyzed in the previous section, is a four-population dynamical system.  
We analyzed this model, where the neuron-type populations are functionally-defined as the Pro- and Anti-populations in each hemisphere (left (L) and right (R)), their connectivity is parameterized geometrically  (Fig. \ref{fig:SC}B).
The input-output function of this model is chosen such that the population responses $\mathbf{x} = [x_{LP}, x_{LA}, x_{RP}, x_{RA}]^\top$ are bounded from 0 to 1 as a function $f$ of a dynamically evolving internal variable $\mathbf{u}$.
\textbf{The model responds to the side with greater Pro neuron activation; e.g. the reponse is left if $x_{LP} > x_{RP}$ at the end of the trial.}
The dynamics evolve with timescale $\tau=0.09$ governed by connectivity weights $W$
\begin{equation}
\begin{split}
\tau \frac{d\mathbf{u}}{dt} &= -\mathbf{u} + W\mathbf{x} + \mathbf{h} + d\mathbf{B} \\
\mathbf{x} &= f(\mathbf{u})
\end{split}
\end{equation}
with white noise of variance $\epsilon^2 = 0.2^2$.
The input $\mathbf{h}$ is comprised of a cue-dependent input to the Pro or Anti populations, a stimulus orientation input to either the Left or Right populations, and a choice-period input to the entire network (see Section \ref{methods_SC}).
Here, we use EPI to determine the changes in network connectivity $\mathbf{z} = [sW, vW, dW, hW]^{\top}$ resulting in execution of rapid task switching behavior.

@@

We define rapid task switching behavior as accurate execution of each task.  Inferred models should not exhibit fully random responses (50\%), or perfect performance (100\%), since perfection is never attained by even the best trained rats.
\textbf{We formulate rapid task switching as an emergent property by stipulating that the average accuracy in the Pro task $p_P(\mathbf{x}, \mathbf{z})$ and Anti task $p_A(\mathbf{x}, \mathbf{z})$ be $75\%$ with variance $5\%^2$.}
\begin{equation}\label{eq:EP}
\begin{split}
\mathcal{X} ~~:~~ \mathbb{E}_{\mathbf{z}}\begin{bmatrix} p_P(\mathbf{x}; \mathbf{z}) \\ p_A(\mathbf{x}; \mathbf{z}) \end{bmatrix}  &~~=~~  \begin{bmatrix} 75\% \\ 75\% \end{bmatrix}  \\ 
 \text{Var}_{\mathbf{z}}\begin{bmatrix} p_P(\mathbf{x}; \mathbf{z}) \\ p_A(\mathbf{x}; \mathbf{z}) \end{bmatrix}  &~~=~~  \begin{bmatrix} 5\%^2 \\ 5\%^2  \end{bmatrix}
\end{split}
\end{equation}
A variance of $5\%$ performance in each task will confer a posterior producing performances ranging from about $65\%-85\%$, allowing us to examine the properties of connectivity that yield better performance.

@@

\textbf{In agreement with experimental results form Duan et al., we found that inactivation above nominal strength during the delay period consistently decreased performance in the Anti task, but had no consistent effect on the Pro task (Fig. \ref{fig:SX3}), e.g. (Fig. \ref{fig:SC}D, bottom).
This difference in resiliency across tasks to delay perturbation is a prediction made by the inferred EPI distribution, rather than an emergent property that was conditioned upon.}
Interestingly, the trends in eigenvalues that result in greater $p_A$ increase the error from delay period inactivation in the Anti task ($p_A - p_{A, opto}$) (Fig. \ref{fig:SC}E.
Despite these opposing effects, $p_A$ is uncorrelated with ($p_A - p_{A, opto}$), while $p_P$ is correlated (Fig. \ref{fig:SX4}).
\textbf{This shows that the connectivity mechanisms that decrease $p_A$ during delay period inactivation are the same mechanisms producing greater $p_P$ during no activation (namely $\lambda_{\text{task}}$ and $\lambda_{\text{side}}$).}
Such comparable dynamics between the non-inactivated Pro task and the delay period inactivated Anti task are salient in simulations (Fig. \ref{fig:SC}D top-left and bottom-right).
